Analysis of competitive surfing tournaments with generalized Bradley-Terry

### 2021-08-25 inst/surfing_jsa.tex
tweaks

We discuss and assess the ``Brazilian storm'' phenomenon using reified
Bradley-Terry techniques, and show that there is no strong evidence to
support the supposed Brazilian preference for point and beach break
beaches.  We also find no evidence to suggest that surfing's being
included in the 2020 Summer Olympics results in modified strategies to
bolster intranational ranking at the expense WCT performance.

Further work might include statistical investigation of noncompetitive
NASH STUFF compatriot priority infringements between compatriots.

>>>>

We discuss and assess the ``Brazilian storm'' phenomenon using reified
Bradley-Terry techniques, and show that there is no strong evidence to
support the supposed Brazilian preference for point and beach break
beaches.  We also find no evidence to suggest that surfing's being
included in the 2020 Summer Olympics results in modified strategies to
bolster intranational ranking at the expense of WCT performance.

Further work might include incorporation of more tournament results
into our likelihood function, and possibly to investigate priority
infringements between compatriots.
